### 2020-11-12 thesis/thesis.tex
rearrange appendices
remove url in bib

% Bib style
\usepackage[
  style=authoryear,
  giveninits=true,
  maxcitenames=2,
  mincitenames=1,
  maxbibnames=21,
  minbibnames=19,
  isbn = false,
  backend=biber,
  uniquelist = false,
  natbib=true
]{biblatex}

@@

% Appendix
%\ETDAppendix{Chapter I Supplementary Material}{
%\input{appendix_1}
%}
\include{thesis/appendix_1}
\include{thesis/appendix_2}
\include{thesis/appendix_3}

>>>>

% Bib style
\usepackage[
  style=authoryear,
  giveninits=true,
  maxcitenames=2,
  mincitenames=1,
  maxbibnames=11,
  minbibnames=10,
  isbn = false,
  backend=biber,
  uniquelist = false,
  natbib=true,
  url=false
]{biblatex}

@@

% Appendix
%\ETDAppendix{Chapter I Supplementary Material}{
%\input{appendix_1}
%}
\include{thesis/appendix_1}
\include{thesis/appendix_2}
\include{thesis/appendix_3}
\include{thesis/appendix_4}
